Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-01-06 stp/paper_aaai/main.tex
update paper

\end{tikzpicture}
\caption{Example of ontology
(`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\protect\tikz{ \protect\path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has an object property'', 
`\protect\tikz{ \protect\path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
means ``has a data property'' and 
`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Example by
\protect\citeasnoun{Taheriyan2013}.
}
\label{FIG:onto}
\vspace{-3mm}
\end{figure}

>>>>

\end{tikzpicture}
\caption{Example of ontology
(`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\protect\tikz{ \protect\path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has an object property'', 
`\protect\tikz{ \protect\path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
means ``has a data property'' and 
`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``subClassOf'' ). Example by
\protect\citeasnoun{Taheriyan2013}.
}
\label{FIG:onto}
\vspace{-3mm}
\end{figure}
